\section{Related Work}\label{sec:relatedwork}
A great amount of work has been done in comparing the transport protocols, TCP and UDP. 

In \cite{giannoulis2009tcp} a performance evaluation of TCP and UDP is done on wireless multihop networks. The results of the evaluation shows clearly that TCP is a more power consuming protocol than UDP. Moreover it shows that UDP is faster and can send more data packets than TCP.

In \cite{bandyopadhyay2013lightweight} a comparison is made between among others CoAP and HTTP which both are web transfer protocols, running two different transport protocols. The experiments in this comparison shows as expected that CoAP has the least number of bytes transferred, due to the overhead in the HTTP header and the connection establishment in TCP.

%These comparisons all clearly shows that TCP is more secure than UDP  but at the same time that TCP has a bigger overhead and thereby is more consuming than UDP.

%comparison of Ligthweight protocols
%Another area which is related is the comparison of  
Lightweight protocols are important for constrained environments, and the comparison of it has been in focus in recent research.
CoAP and MQTT are compared in \cite{bandyopadhyay2013lightweight} in an IoT context using constrained gateway devices. The results of this comparison shows that CoAP is most efficient in terms of energy consumption as well as bandwidth.

Another research \cite{de2013comparison} also compares CoAP with MQTT but for Smartphone usage. The comparison shows that CoAP, in certain application scenarios, can be a valid alternative for MQTT, which already has been used for Smartphone solutions.

CoAP over TCP is new and few has worked with it, but until now no one has made a comparison between it and the original CoAP which runs over UDP. 
Furthermore, the comparisons of the UDP and TCP did not consider the aspect of constrained environments and the suitability of running lightweight protocols.